Wind veer and and Speed in Turbulent Ekman Flow

### 2022-01-11 write1/manuscript.tex
inserted some references; more to come

More recently, \citet{ghannam:jas2021} treated the horizontally averaged momentum budget to show that departures from

@@

approach around the base state\citep{momen:jas2016}; 

@@

the height-dependence of the veer and stress misalignment \citep{momen:jas2018, ghannam:jas2021}.

>>>>

More recently, \citet{ghannam:QJR2021} treated the horizontally averaged momentum budget to show that departures from

@@

approach around the base state\citep{momen:JAS2016}; 

@@

the height-dependence of the veer and stress misalignment \citep{momen:JAS2018, ghannam:QJR2021}.
